Summer 2025 ToDo

### 2025-09-07 Relations/Paper/Summer_2025_TODO.tex
added comment about isWFCor

>>>>

\section*{September 2025}
\subsection*{Notes from 7th September}
Thoughts on the current state of the paper.
\begin{description}
\item[The status of wfCor]
  \begin{itemize}
    \item 
      On the ``missing'' implication isWFCor$\lnot\lnot$ to isWFminDNE$\lnot\lnot$.

      The wfCor hypothesis needs a ``choice function'' that will pick a successor $y$ of a given element $x$
      (while still refuting the given predicate).

      The property wfMinDNE$\lnot\lnot$ is equivalent to the statement that, if a $\lnot\lnot$-closed 
      predicate $P$ has no minimal element, then its complement is universally true.

      The ``no minimal element'' for not-not-closed $P$ is close to saying that its complement is coreductive; 
      the difference is precisely that between the ``strong'' existential in the coreductive statement ---
      and the weak one (with $\lnot\lnot$ applied to it) in the minimality one.

      Assuming finite branchingness and weak decidability of $P$, we could get the strong existential 
      from the weak one.  However, weak decidability and DNE are already equivalent with EM, so that 
      will only apply to decidable predicates.  There may be a relationship to isWFminEM, but that 
      would be a question for another paper.

    \item 
      On the ``strong side'' of the WF diagram, the situation is even worse.
      Neither implication between isWFCor and isWFminDNE is provable, and similarly for isWFCor and isWFSeq.

    \item 
      At this point, there does not appear to be much more to say isWFCor, so we should consider removing it.

      On Monday, we should quickly discuss the different versions of sequentially,
      and move on to writing the text of the paper.
    \end{itemize}
\end{descriptioni}
